Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-07 Writing/CEA_2nd_round/replies_rev_1.rmd

**Materials and Method to just Method: Monte Carlo Simulations?**

We do see a redundancy of expalining how CF can be used to identify site-specific input recommendations. It is explained twice in 2.2 and 3.2.2, while 2.2 is intended for a more general case than 3.2.2 that is specific to our simulations. Therefore, we decided to take out 2.2. We also renamed 2.1 to "Estimating EOIR and Treatment Effects"

We have moved an example of causal tree (previously in seciton 2.3), but decide to keep the explanation of how CF works. The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations. To this core objective, ML simulations are our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal. However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Instead of this, we believe that it is beneficial to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted. Therefore, we kept 2.3 and 2.4 in the current manuscript.

@@

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our current manuscript is appropriate and it is hard for us to further slim down the section. Moreover, we believe we no longer have any redundancy in this section any more.

@@

It is degree. The unit is now provided in Appendix A.

@@

<span style="color:blue">  
All the formulas are now numbered. 
</span>

@@

Trainign dataset and test dataset are completely separate. Models are trained on the entirety of the train data for each simulation, and then the trained model is tested against a test dataset that are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$. The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters at each simulation round.

@@

**8. I can’t open the code link (https://github.com/tmieno2/ML_VRA.git, lines 199 and 249) with my browsers (chrome, edge, and Firefox). Please upload the code to the public research data repositories (Zenodo, Mendeley Data, figshare, Harvard Dataverse, etc.), not GitHub. Please generate a separate DOI for your code and cite it.**

<span style="color:blue">  
We realized that the github repository was private and that was why you were not able to access it. We made a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).

The simulation codes and the data were also shared on Mendeley Data (<span style = "color: blue;"> Shun, provide the link here </span>) according to the Editor's suggestion for the ease of access. The link is also provided <span style = "color: blue;"> Shun, be speficic about where it is </span>.

**9. Please convert the length units of the manuscript to international length units. (line 207)**
<span style="color:blue">

All the lenth units were converted to meter (m)

**10. Please add the number of rows and columns to the plots, subplots, and cells schematics in Figure 2. (line 209)**
<span style="color:blue">

The number of rows and columns of plots, subplots, and cells schematics are now indicated Figure 2.
</span>

@@

**12. The titles of 4.1 and 4.2 are confusing, please revise. (lines 410 and 457)**
<span style="color:blue">

The title of 4.1 was changed to "Comparison of EONR estimation accuracy" to reflect its contents. The title of section 4.2 was changed to "The relationship between yield and EONR prediction performances". 
</span>

**13. Why there are no CNN results in Figures 8,9, and 10? (lines 439, 441, and 453)**
<span style="color:blue">

+ As explained in section 4.1, CNN completely failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1). Therefore, I do not think that visualizing the CNN results provide any meaningful implications to understand its performance of EONR estimation performance.
+ I added the explanation for not showing CNN results in Figures 8,9, and 10. ("CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively")

**14. I suggest that the authors add to the supplementary material a table of the training accuracy of the different models.**
<span style="color:blue">

+ run simulations on training dataset, and report the results.
</span>

@@

@@

>>>>

We do see a redundancy of expalining how CF can be used to identify site-specific input recommendations. It was explained twice in 2.2 and 3.2.2, while 2.2 is intended for a more general case than 3.2.2 that is specific to our simulations. Therefore, we decided to take out 2.2. We also renamed 2.1 to "Estimating EOIR and Treatment Effects."

We have moved an example of causal tree (previously in seciton 2.3), but decide to keep the explanation of how CF works. The core objective of the paper is to test the CF against existing ML methods in predicting EOIR and economic performance of resulting site-specific input use recommendations. To this core objective, ML simulation is our core method. For this reason, in our Materials and Methods section, we would like to avoid the explanation of how CF works just like we do not give too much explanations to any of RF, BRF, and CNN, which are well-established and mostly understood already by the readers of this journal. However, since this article is the first to apply CF in the field of agronomy, let alone site-specific input management, we believe that it is worthwhile to present how it works in detail and what conditions are necessary for it to work well. Now, if we place such description inside the Materials and Method section, it will break the flow of explaning how MC simulations work, temporarily distracting readers from how MC simulations are conducted to the details of how CF works. Insted, we believe that it is better to first give readers knowledge on how CF works and the potential advantages over the existing predition-oriented ML methods as essential knowledge before we move onto how our MC simulations are conducted in the Materials and Method section, in which we would like to focus on how MC simulations are conducted. Therefore, we kept 2.3 and 2.4 (in the previous round) in the current manuscript.

@@

In MC simulation studies, we believe that presenting how data is generated in detail is crucial because the results are dependent on how data is generated. It is much like any emprical studies using real experiment data provides lots of details about the experiemnts. We take reproducibility seriously and we believe that the details we peovided in our current manuscript is appropriate and it is hard for us to further slim down the section. Moreover, we believe we no longer have any redundancy in this section.

@@

It is degree. The unit is now provided in the description of the figure in Appendix A. Please not that this example is just for illustrating how CF works.

@@

<span style="color:blue">  
All the formulas are now numbered. <span style = "color: blue;"> Shun, make sure this happens right before you submit. </span>
</span>

@@

Trainign dataset and test dataset are completely separate. For a given simulation round, training dataset in another round of simulation acts as a "test" dataset. The "test" dataset are created independently from one another and are different in the underdyling field parameters $\alphe$, $\beta$, and $ymax$. Therefor, in MC simulations, a dataset in a given simulation serves as a train data, and served as a test data for another simulation round. The train dataset, however, was split into several parts when cross-validation was performed in determing the optimal hyperparameters within a given simulation round.

@@

**8. I can't open the code link (https://github.com/tmieno2/ML_VRA.git, lines 199 and 249) with my browsers (chrome, edge, and Firefox). Please upload the code to the public research data repositories (Zenodo, Mendeley Data, figshare, Harvard Dataverse, etc.), not GitHub. Please generate a separate DOI for your code and cite it.**

<span style="color:blue">  
The simulation codes and the data were also shared on Mendeley Data (<span style = "color: blue;"> Shun, provide the link here </span>) according to the Editor's suggestion for the ease of access. The link is also provided <span style = "color: blue;"> Shun, be speficic about where it is </span>.

<span style = "color: blue;"> Shun, make sure you cite the code and data. </span>

We realized that the github repository was private and that was why you were not able to access it. We made a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
</span>

**9. Please convert the length units of the manuscript to international length units. (line 207)**

<span style="color:blue">  
All the lenth units were converted to meter (m)
</span>

**10. Please add the number of rows and columns to the plots, subplots, and cells schematics in Figure 2. (line 209)**

<span style="color:blue">  
The number of rows and columns of plots, subplots, and cells schematics are now indicated Figure 2.
</span>

@@

**12. The titles of 4.1 and 4.2 are confusing, please revise. (lines 410 and 457)**

<span style="color:blue">  
The title of 4.1 was changed to "Comparison of EONR estimation accuracy" to reflect its contents. The title of section 4.2 was changed to "The relationship between yield and EONR prediction performances". 
</span>

**13. Why there are no CNN results in Figures 8,9, and 10? (lines 439, 441, and 453)**

As explained in section 4.1, CNN failed to predict site-specific EONR because the estimated yield response function were always linear (please see the Table 1). Consequently, I do not think that visualizing the CNN results provide any meaningful implications to understand its performance of EONR estimation performance.

+ I added the explanation for not showing CNN results in Figures 8,9, and 10. ("CNN is not shown as its RMSEs of the EONR estimations and $\hat{\pi}_{def}$ always take $62.8$ kg/ha and \$$58.99$/ha, respectively")
</span>

**14. I suggest that the authors add to the supplementary material a table of the training accuracy of the different models.**

<span style="color:blue">  
+ run simulations on training dataset, and report the results.
</span>

@@

<span style="color:blue">  
We added a new section called "Limitations and Future Studies" before the Conclustion section. One of the important assumptions that needs to be satisfied for CF to provides consistent estimation of treatment effects is that the treatment (N rates here) is uncorrelated with unobservable characteristics. Other assumtions are relatively minor. Note that, this is not just for CF, but also for RF, BRF, and CNN. Whenever the variable of interest (N rates here), their estiamtion of its impact on the dependent variable is biased in general. Fortunatley, in OFPE settings, we can randomize or patternize the input rates in a way that the input rates are uncorrelated to the unobserved variables. Therefore, the violation of this assumption is not as much of a concener as in a setting where observational data is used. We discuss these in the "Trial Design and Yield Data Generation for Modeling" section. 
</span>

@@

<span style="color:blue">  
We moved the descriptions of the limitations (uncertainty) of the study to a separate section as mentioned earlier in our reply to your comment 14.
</span>

### 2022-02-07 Writing/appendix.rmd

# Appendix B: Parameter Generation

## Base parameters $\alpha$, $\beta$, and $ymax$ {#par-gen}
Parameters $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model. The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose

Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha^{i,j}$, $\beta^{i,j}$, $ymax^{i,j}$, and $\varepsilon^{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project. (Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) The range and nugget of all parameters were assumed to be $400$ m and 0. The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$. See Figure \@ref(fig:fig-parameters) for an example of the generated parameters.

```{r fig-optN, fig.width=3, fig.height=4, fig.cap = "An illustrative example of a spatial distribution of true optimal N rate"}

vis_optN_cell
```

```{r fig-parameters, fig.width=6, fig.height=5, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}
# field_alpha + field_beta + field_ymax
grid.arrange(field_ymax, field_alpha, field_beta, field_m_error, ncol = 2, nrow = 2)
```

@@

For scenarios "aabbyy" and "aabbyytt", each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner. Speficiallu, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r_{\alpha}^{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r_{\beta}^{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r_{ymax}^{i,j} \in (0,1)$ to the ${ymax}^{i,j}$ variable. Each of the weight variables are generated using unconditional Gaussian geostatistical simulation just like the base parameters. (There was no spatial correlation between the $r_{\alpha}^{i,j}$ and $r_{\beta}^{i,j}$ data, between $r_{\alpha}^{i,j}$ and $r_{ymax}^{i,j}$ data, or between $r_{\beta}^{i,j}$ and $r_{ymax}^{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha^{i,j}$, $\beta^{i,j}$ and $ymax^{i,j}$. These were 
$\alpha_{1}^{i,j} = r_{\alpha}^{i,j} \alpha^{i,j}$, $\alpha_{2}^{i,j} = (1- r_{\alpha}^{i,j}) \alpha^{i,j}$,
$\beta_{1}^{i,j} = r_{\beta}^{i,j} \beta^{i,j}$, $\beta_{2}^{i,j} = (1- r_{\beta}^{i,j}) \beta^{i,j}$,
$ymax_{1}^{i,j} = r_{ymax}^{i,j} ymax^{i,j}$, and $ymax_{2}^{i,j} = (1- r_{ymax}^{i,j}) ymax^{i,j}$. The codes used to implement the abovementioned parameter splitting is available at https://github.com/tmieno2/ML_VRA.git.

>>>>

# Appendix B: Understanding yield response functions better

Another way to writing Eq. \@ref(eq:eqn6) that may help understanding the yield response (Eq. \@ref(eq:eqn6)) better conceptually is as follows:

\begin{alinged}
f(N, \mathbf{c}) = ymax(\mathbf{c})(1-exp(\alpha(\mathbf{c}) + \beta(\mathbf{c}) N)) + \varepsilon. 
\end{alinged}

In this formulation, it is made clear that the base parameters $\alpha$, $\beta$, and $ymax$ are functions of a vector of field characteristics variables $\mathbf{c}=(c_1,\dots,c_K)$, which vary spatially on the field.

Which of $c_1,\dots,c_K$ has an influence vary by the parameters. For example, $\alpha$ represents what the yield would be when no nitrogen is applied in conjunction with $ymax$ because when $N = 0$, $yield = ymax * (1-exp(\alpha))$. So, $\alpha$ is a function of soil organic matter and residual nitrogen among $\mathbf{c}$. $ymax$ determines the maximum yield attainable. So, $ymax$ is a function of other micro nutrients like phosphorus and soil depth among $\mathbf{c}$. $\beta$ reflects how efficiently the crop uses N to create grain mass. So, it may be a function of soil properties that affect the availability of applied N fertilizer to the crop, such as N immobilization, leaching, denitrification, and volatilization among $\mathbf{c}$.

Each subplot has different values of $\mathbf{c}$, and yield at the subplot level can be written as

\begin{equation}
f(N_{i}, \mathbf{c}_{i}) = ymax(\mathbf{c}_{i})(1-exp(\alpha(\mathbf{c}_{i}) + \beta(\mathbf{c}_{i}) N_{i})) + \varepsilon_{i}. 
\end{equation}

The simplified notation of this equation, where $c_i$ is dropped, is \@ref(eq:eqn6) in section <span style = "color: blue;"> section number here </span>.

<span style = "color: blue;"> Shun, number the equations </span>

# Appendix C: Parameter generation

## Base parameters $\alpha$, $\beta$, and $ymax$ {#par-gen}
Parameters $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$ were modeled as spatially autocorrelated using unconditional Gaussian geostatistical simulation based on the spherical variogram model. The `gstat` package (version 2.0.6 [@gstat1; @gstat2]) in R was used for this purpose

Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project. (Codes used to generate parameter values are available at https://github.com/tmieno2/ML_VRA.git.) The range and nugget of all parameters were assumed to be $400$ m and 0. The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$. See Figure \@ref(fig:fig-parameters) for an example of the generated parameters.

<span style = "color: blue;"> Shun, combnine all the figures </span>

```{r variogram-parameters, tab.cap = "The Parameters for the Variogram Models"}
variogram_tb
```

```{r fig-parameters, fig.width=7, fig.height=9, fig.cap = "An Illustrative Example of Spatial Distributions of Field Characteristics", cache = TRUE}

field_alpha + field_beta + field_ymax + field_m_error + vis_optN_cell + plot_layout(ncol = 2)
```

@@

For scenarios "aabbyy" and "aabbyytt", each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner. Speficiallu, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r^{\alpha}_{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r^{\beta}_{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r^{ymax}_{i,j} \in (0,1)$ to the ${ymax}_{i,j}$ variable. Each of the weight variables are generated using unconditional Gaussian geostatistical simulation just like the base parameters. (There was no spatial correlation between the $r^{\alpha}_{i,j}$ and $r^{\beta}_{i,j}$ data, between $r^{\alpha}_{i,j}$ and $r^{ymax}_{i,j}$ data, or between $r^{\beta}_{i,j}$ and $r^{ymax}_{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha_{i,j}$, $\beta_{i,j}$ and $ymax_{i,j}$. These were 
$\alpha_{1}_{i,j} = r^{\alpha}_{i,j} \alpha_{i,j}$, $\alpha_{2}_{i,j} = (1- r^{\alpha}_{i,j}) \alpha_{i,j}$,
$\beta_{1}_{i,j} = r^{\beta}_{i,j} \beta_{i,j}$, $\beta_{2}_{i,j} = (1- r^{\beta}_{i,j}) \beta_{i,j}$,
$ymax_{1}_{i,j} = r^{ymax}_{i,j} ymax_{i,j}$, and $ymax_{2}_{i,j} = (1- r^{ymax}_{i,j}) ymax_{i,j}$. The codes used to implement the abovementioned parameter splitting is available at https://github.com/tmieno2/ML_VRA.git.

<span style = "color: blue;"> Shun, provide the link to Mandeley data and cite it </span>
